%  Creating a Quick Report with knitr, xtable, R Markdown, Pandoc (and some OpenBLAS Benchmark Results)

# Summary of data

The following is an analysis of readings and outliers of SharedSolar 
energy consumption data grouped by site and month.  

The sql used to generate the input file can be found in the 
[shared_solar_data_warehouse/sql](https://github.com/SEL-Columbia/shared_solar_data_warehouse/tree/master/sql)
repository.  

# Set up the data

Load the csv and filter out all non-site level rows

```{r echo=TRUE, message=FALSE, results='asis', prompt=FALSE, dpi=600}
reads_outs <- read.csv('reads_outliers_monthly.csv')

reads_outs <- subset(reads_outs, ip_addr=='192_168_1_200' & !(site_id %in% c('ug01', 'ug02', 'ug05')))

reads_outs$month_as_date <- as.Date(reads_outs$time_stamp)
reads_outs$outs_percent <- reads_outs$outliers / reads_outs$readings

reads_outs <- subset(reads_outs, month_as_date > as.Date('2011-01-01'))
```

# Plot the outliers and % outliers of total

```{r echo=FALSE, message=FALSE, results='asis', prompt=FALSE, dpi=600, fig.width=8, fig.height=5, fig.cap="Benchmark Results Comparison"}
                                 
library(ggplot2)
library(scales)
ggplot(data = reads_outs, aes(month_as_date, fill = site_id)) + 
  geom_bar(aes(weight=outs_percent)) + 
  scale_x_date(labels=date_format("%b/%y")) +
  xlab("Month") +
  ylab("Percent Outliers of Total")

```
